---
title: "Robustness and sensitivity"
---

```{r}
#| include: false
read_table <- function(name) utils::read.csv(file.path("outputs/tables", name), check.names = FALSE)
```

## Bootstrap

The OLS model is resampled 2,000 times with a fixed seed. Percentile intervals provide a distributional sensitivity check rather than a new estimand.

```{r}
knitr::kable(read_table("bootstrap_ols_2000.csv"), digits = 4)
```

## Influence diagnostics

```{r}
knitr::kable(read_table("influence_summary.csv"))
```

Individual-level influence diagnostics are generated under `outputs/restricted/` and are intentionally omitted from the rendered public-facing report.

## Chi-square sensitivity

The Figshare package does not document the exact SPSS crosstab definitions. The repository therefore does **not** claim to reconstruct an unspecified original chi-square table. Instead, it exposes one reproducible sensitivity definition: rounded construct mean (1–5) crossed with rounded Green Finance Adoption mean (1–5).

```{r}
knitr::kable(read_table("chi_square_construct_sensitivity.csv"), digits = 4)
```

Expected cell counts should be inspected before interpreting asymptotic p-values. Item-level sensitivity outputs include Benjamini-Hochberg FDR adjustment.
