---
title: "SPSS source reconciliation"
---

```{r}
#| include: false
read_table <- function(name) utils::read.csv(file.path("outputs/tables", name), check.names = FALSE)
```

## Raw item consistency

The R pipeline reads `Dataset_S2_SPSS_Data_File.sav` with `haven` and verifies that V1–V30 match the Excel raw-data sheet exactly.

```{r}
knitr::kable(read_table("spss_file_validation.csv"), digits = 10)
```

## Composite-score consistency

The Figshare README documents five SPSS composite columns. The repository recomputes those scores directly from V1–V30 and checks the maximum absolute difference against the corresponding `.sav` columns.

```{r}
knitr::kable(read_table("spss_composite_reconciliation.csv"), digits = 12)
```

## Boundary

`Dataset_S3_SPSS_Output.spv` is preserved unchanged as the original SPSS viewer output. This repository does not parse the proprietary viewer file or transplant numbers from it. Reproducibility is established from the raw XLSX and direct `.sav` consistency checks.
